Stack Safety is a Security Property

### 2021-04-17 tex/main.tex
Rephrase PBT in intro + NITS

In the present work, we also describe the protection of both stack data (like LSE) and
control flow (like WBCF).  Our technical formulation of WBCF is similar to
theirs, but our treatment of stack data protection is rather different,
as is our approach to the definition itself. Instead of defining stack safety implicitly,
as ``what a certain idealized machine does,'' we give an
\emph{explicit} definition using the technical framework of language-based
security\ifaftersubmission~\citep{??}\bcp{Maybe the Sabelfeld and Myers
  survey?}\fi, phrased as the conjunction of
\emph{stack integrity} and \emph{stack confidentiality}.
%
A key technical novelty in these definitions,
compared to standard formulations of confidentiality and integrity from the
security literature, is that they
are ``nested'': {\em each} caller is guaranteed protection from its
immediate callees (which, in turn, need protection from their immediate
callees, etc.). They are also stronger than LSE; even in the absence of the
control flow guarantees of WBCF, they guarantee callers'
data safety in the face of control-flow attacks (see \cref{sec:controlflow}).
\rb{Reference to \cref{sec:running-example}, where this is discussed now?}
This reflects an arguably cleaner division between data protection and
control-flow protection than LSE / WBCF.

For confidentiality and integrity , we consider both {\em stepwise}
and {\em observational} variants.  The simpler stepwise
variants formalize the intuition that a caller's local data is {\em never}
read or modified during a call. The observational variants
allow a callee to read from and write to their caller's stack frame, as
long as nothing that they read affects their observable behavior and nothing
they write affects the observable behavior of the caller after they return.
The observational properties are meant to capture the same sense of security,
extensionally enough that any reasonable protection mechanism ought to enforce
them, even if it does not prevent every single dangerous read or write.

@@

To demonstrate the utility of our formal characterization, we use these
properties to validate and improve an existing enforcement mechanism, the
{\em stack-safety micro-policies} of~\citet{DBLP:conf/sp/RoesslerD18}.  We
use QuickChick~\citep{Denes:VSL2014,Pierce:SF4}, a property-based testing
tool for the Coq proof assistant, to generate many random programs and check
that Roessler and Dehon's micro-policies correctly abort the ones that
attempt to violate one of our properties; furthermore, we introduce several
intentionally broken micro-policies and check that the testing framework is
able to generate counterexamples that violate our properties but are not
halted by the incorrect enforcement variants.  (Showing that the testing
framework detects intentional bugs in enforcement mechanisms increases our
confidence that it can also catch unknown ones, strengthening our confidence
in the enforcement mechanism itself.\ifaftersubmission\bcp{Maybe that
  sentence belongs in the testing section?}\fi)

>>>>

In the present work, we also describe the protection of both stack data (like LSE) and
control flow (like WBCF).  Our technical formulation of WBCF is similar to
theirs, but our treatment of stack data protection is rather different,
as is our approach to the definition itself. Instead of defining stack safety implicitly,
as ``what a certain idealized machine does,'' we give an
\emph{explicit} definition using the technical framework of language-based
security\ifaftersubmission~\citep{??}\bcp{Maybe the Sabelfeld and Myers
  survey?}\fi, phrased as the conjunction of
\emph{stack integrity} and \emph{stack confidentiality}.
%
A key technical novelty in these definitions,
compared to standard formulations of confidentiality and integrity from the
security literature, is that they
are ``nested'': {\em each} caller is guaranteed protection from its
immediate callees (which, in turn, need protection from their immediate
callees, etc.). They are also stronger than LSE; even in the absence of the
control flow guarantees of WBCF, they guarantee callers'
data safety in the face of control-flow attacks (see \cref{sec:controlflow}).
%\rb{Reference to \cref{sec:running-example}, where this is discussed now?}
This reflects an arguably cleaner division between data protection and
control-flow protection than LSE / WBCF.

For confidentiality and integrity, we consider both {\em stepwise}
and {\em observational} variants.  The simpler stepwise
variants formalize the intuition that a caller's local data is {\em never}
read or modified during a call. The observational variants
allow a callee to read from and write to their caller's stack frame, as
long as nothing that they read affects their observable behavior and nothing
they write affects the observable behavior of the caller after they return.
The observational properties are meant to capture the same sense of security,
extensionally enough that any reasonable protection mechanism ought to enforce
them, even if it does not prevent every single dangerous read or write.

@@

To demonstrate the utility of our formal characterization, we use these
properties to validate and improve an existing enforcement mechanism, the
{\em stack-safety micro-policies} of~\citet{DBLP:conf/sp/RoesslerD18}, re-implemented
in the Coq proof assistant on top of a RISC-V specification.  We
use QuickChick~\citep{Denes:VSL2014,Pierce:SF4}, a property-based testing
tool for Coq, to generate many random programs and check
that Roessler and Dehon's micro-policies correctly abort the ones that
attempt to violate one of our properties; furthermore, we
%
check that the testing framework is able to generate counterexamples
that violate our properties but are not halted by incorrect
enforcement variants (both variants that we accidentally created
during our re-implementation of the micro-policy and ones that we
intentionally crafted to be broken in order to increase our confidence
in testing and the enforcement mechanism itself).
%introduce several
%intentionally broken micro-policies and check that the testing framework is
%able to generate counterexamples that violate our properties but are not
%halted by the incorrect enforcement variants.  (Showing that the testing
%framework detects intentional bugs in enforcement mechanisms increases our
%confidence that it can also catch unknown ones, strengthening our confidence
%in the enforcement mechanism itself.\ifaftersubmission\bcp{Maybe that
%  sentence belongs in the testing section?}\fi)
